\bf Estimating the number of clusters using cross-validation

### 2017-02-08 cvclust.tex
add acknowledgements

>>>>

\section*{Acknowledgements}

We thank Rob Tibshirani for getting us started on this problem and
for providing code for some initial simulations. We thank Art~Owen for
providing us with a summary of the relevant theory on $k$-means clustering,
and for giving us feedback on our theoretical results.  We also thank Cliff
Hurvich, Josh Reed, and Jeff~Simonoff, for providing comments on an early
draft of this manuscript and for suggesting further avenues of inquiry.
